\mireval{}

### 2014-05-06 paper/paper.tex
fix mirex acronym, add couple of sentences to melody discussion about resampling

% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
For the past 10 years, the yearly Music Information Retrieval EXchange (MIREX) has provided setting in which different MIR algorithms are compared over common datasets \cite{downie2008music}.
By providing a standardized shared-task setting to track progress, MIREX has proven to be critically useful in the evolution of MIR research.
MIREX relies on the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
The NEMA codebase includes multiple programming languages and dependencies (including proprietary ones, e.g. MATLAB) so compiling and running it for research uses is nontrivial.

@@

For this reason, the melody evaluator in \mireval{} uses $1^{st}$-order (linear)
interpolation by default in order to map the reference and estimate sequences
onto a common time-grid. Assuming the original timestamps of both sequences
correspond to the \textit{center} of each analysis frame (as they should),
using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
returned by \mireval{} are lower-bounded by the MIREX results and are, in our
view, more accurate.

>>>>

% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
For the past 10 years, the yearly Music Information Retrieval Evaluation eXchange (MIREX) has provided setting in which different MIR algorithms are compared over common datasets \cite{downie2008music}.
By providing a standardized shared-task setting to track progress, MIREX has proven to be critically useful in the evolution of MIR research.
MIREX relies on the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
The NEMA codebase includes multiple programming languages and dependencies (including proprietary ones, e.g. MATLAB) so compiling and running it for research uses is nontrivial.

@@

For this reason, the melody evaluator in \mireval{} uses $1^{st}$-order (linear)
interpolation by default in order to map the reference and estimate sequences
onto a common time-grid. Assuming the original timestamps of both sequences
correspond to the \textit{center} of each analysis frame (as they should),
using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
returned by \mireval{} are lower-bounded by the MIREX results and are, in our
view, more accurate. By default, the estimate is resampled using the reference's
time grid so that the reference can be used without any modification.
Alternatively, the user can specify a hop size, in which case both
reference and estimate are resampled onto the new time-grid defined by the hop
size.
